\documentclass[a4paper,11pt]{moderncv}

% moderncv themes
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and
% 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[orange]{classic}

% for web links
\definecolor{href}{rgb}{0.2,0.4,0.65}
\newcommand\weblink[2] {{\color{href} \href{#1}{#2}}}
\newcommand\cvskill[2] {\cvline{#1}{
\begin{minipage}[t]{%
  \linewidth}\small #2
\end{minipage}
}}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\AtBeginDocument{\recomputelengths}

% personal data
\firstname{Angel}
\familyname{Freire}
\title{Software architect}
\address{Nepper 1039}{C1406DUA Capital Federal, Argentina}
\phone{+54 11 6379 9160}
\mobile{+54 11 9 6585 3302}
\email{cuerty@gmail.com}
\homepage{https://ar.linkedin.com/in/angelfreire}

\nopagenumbers{}

\begin{document}
\maketitle

\section{Profile}
I'm a self--taught programmer and team leader that is constantly striving to
learn new things and love to work to get things right, make things better, and,
more importantly, get things done.\\

I've a strong knowledge of several programming languages. Most of this
knowledge comes from experience working in my daily job or by collaborating on
open source proyects.\\

Finally I'm proactive, quick--learner and goal oriented.\\

\section{Professional Expertise}
\begin{itemize}
\item Deep web development knowledge, ranging from backend programming in
  Ruby, Python and PHP to frontend programming using JavaScript and HTML + CSS.
  Knowledge of backend frameworks (Django, Flask) and frontend libraries
  (jQuery, Backbone.js, Angular, Flux/React). Prefer backend rather than
  frontend programming.
\item Object--oriented design and programming.
\item Strong practical knowledge of Python, C++, C, Java and PHP.
\item Strong practical knowledge of relational databases, more specific
  PostgreSQL, MySQL, Vertica and Redshift.
\item Strong practical knowledge of cloud solutions. In particular the AWS stack.
\item Strong practical knowledge of mobile development in Android and iOS.
\item Practical knowledge of the non-relational databases Cassandra, Redis and
  Elasticsearch.
\item Practical knowledge of the distributed computing with Hadoop (Cascading)
  and Spark.
\item Practical knowledge of the message brokers solutions including Kafka
  and RabbitMQ.
\item Experience working with the GNU toolchain (gcc, g++, make, autotools,
  etc).
\item Concurrent and network programming, including POSIX threads, BSD sockets,
  TCP/IP and POSIX IPC (Inter--Process Communication) experience.
\item GNU/Linux systems specialist. More than 18 years of experience as user
  and administrator.
\item Practical and theoretical knowledge of networking protocols (IP, TCP/IP,
  UDP, etc.) and application protocols over IP (HTTP, SMTP, POP 3, DNS, SMPP,
  STOMP, AMQP and others).
\item Use and design of web services, including SOAP, XMLRPC and ReST.
\item Use of version control systems: Subversion, Mercurial and GIT.
\item Configuration, administration and use of Continuous Integration
Solutions: Buildbot and Hudson CI (Jenkins CI).
\item Network administration: firewalling (iptables), advanced routing, NAT.
\item Behavior Driven Programming and Test-driven development.
\item Working with some of the most popular agile methodologies (Scrum, XP).
\item Some knowledge of Perl, Ruby, .NET (Microsoft and Mono implementations),
  JavaScript (Node.js), Erlang and Haskell.
\end{itemize}

\pagebreak

\section{Experience}
\cventry{January 2001\\Present}{Freelance programmer}
{Freelance programmer}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Worked on several proyects that include making redistributable
  applications, websites and webservices.
  \item Recent projects:
  \begin{itemize}
    \item \weblink{http://www.datafarming.net}{DataFarming}, backend,
      analitycs platform and mobile applications.
    \item \weblink{http://www.ecos.la}{Ecos}, online newspaper and
      backoffice.
  \end{itemize}
  \item Used Python, C++, MySQL, PostgreSQL, Elasticsearch, Java, Ruby,
    Perl, JavaScript and PHP.
\end{itemize}
}
%
\cventry{June 2018\\Present}{Chief Technical Officer}
{\weblink{https://mgrana.com}{mGrana}}{Buenos Aires, Argentina and São Paulo, Brazil}{}{%
\begin{itemize}
  \item Work on product definition.
  \item Create and define the architecture of the platform.
  \item Design and implementation of the public website, internal backoffice, and external backoffice, including ACL restrictions.
  \item Design, implementation and maintenance of the infrastructure.
  \item Integration of different payment solutions and fraud detection 
    systems.
  \item Used Python, PostgreSQL, Elasticsearch, Javascript and Java.
\end{itemize}
}
%
\cventry{June 2014\\December 2019}{Chief Technical Officer}
{\weblink{https://www.prontochef.com.br}{ProntoChef}}{São Paulo, Brazil}{Remote}{%
\begin{itemize}
  \item Create and define the architecture of the platform.
  \item Design and implementation of the first versions of the public website.
  \item Design, implementation and maintenance of the infrastructure.
  \item Design and implementation of analytics and logistics platforms.
  \item Integration of different payment solutions and fraud detection 
    systems.
  \item Used Python, PostgreSQL, Elasticsearch and Javascript.
\end{itemize}
}
%
\cventry{September 2012\\June 2014}{Chief Architect Officer}
{\weblink{http://www.hotelhoje.com}{Hotel Hoje}}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Create and define the architecture of the Hotel Hoje platform.
  \item Design, implementation and maintenance of the infrastructure.
  \item Build, manage and lead the IT team.
  \item Design and implementation of the Android and iOS applications.
  \item Integration of different payment solutions and fraud detection 
    systems.
  \item Used Python, Java, Riak and PostgreSQL.
\end{itemize}
}
%
\cventry{August 2011\\May 2012}{Analytics Tech Lead}
{\weblink{http://www.vostu.com}{Vostu}}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Responsable for the design and improvement of ETL process.
  \item Design of the Data Warehouse including the provisioning planning and
  the database design.
  \item Design and implementation of the real time tracking platform.
  \item Leaded the process of adding analytics capabilities to the existent
  platforms.
  \item Used Python, C++, Java, Hadoop, Vertica and RabbitMQ.
\end{itemize}
}
%
\cventry{January 2011\\June 2011}{Latam Platforms Tech Leader}
{\weblink{https://www.movile.com}{Movile}}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Responsable for the design and improvement of the company platforms
  used to provide value added services for mobile phones in the LATAM area.
  \item Designed the plan to complete the fusion of the platforms between
  Movile and Cyclelogic.
  \item Used Python, C++, Java, Cassandra, SQL Server, PostgreSQL, RabbitMQ and
  HornetQ.
\end{itemize}
}
%
\cventry{November 2006\\December 2010}{Chief Architect}
{\weblink{http://www.cyclelogic.com}{Cyclelogic}}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Responsible for leading the team in charge of the design, development
  and implementation of company platforms.
  \item Used Python, C++, Delphi, CouchDB, Redis, SQL Server, MySQL, PostgreSQL
  and RabbitMQ.
\end{itemize}
}
%
\cventry{August 2002\\December 2004}{Semi Senior Programmer}
{\weblink{https://www.buenosaires.gob.ar/educacion}{Secretaria de Educación, G.C.B.A}}{Buenos Aires, Argentina}{}{%
\begin{itemize}
  \item Started as a junior programmer and then work as a semi senior programmer on
  several projects.
  \item Used Visual Basic 6, Visual Basic and C\# .NET and many other tools of
  the Microsoft stack.
\end{itemize}
}
%

\section{Contributions to FLOSS Projects}
\cvline{}{Contributed to popular FLOSS (Open--Source) projects including:}
\cvlistdoubleitem{\mbox{\weblink{https://qpid.apache.org/}{Apache Qpid}}}{%
\mbox{\weblink{https://www.djangoproject.com/}{Django}}}
\cvlistdoubleitem{\mbox{\weblink{https://www.python.org/}{Python}}}{%
\mbox{\weblink{https://fluxbox.org/}{Fluxbox}}}

\pagebreak

\section{Education}
\cventry{2001 -- Unfinished}{Licenciatura en Ciencias de la Comunicaci\'on Social}{Facultad de Ciencias Sociales (UBA)}{Argentina}{}{}
\cventry{1996 -- 2000}{Bachiller en Comunicaci\'on social}{Escuela Julio Cort\'azar}{Argentina}{}{}

\section{Training and courses}
\begin{itemize}
\item Introduction to Computing: General management of operating systems and office software. (IBM certified)
\item Programming: Study rationale and practical use of logical programming languages. (Tutor)
\item PostgreSQL: Use and administration. (Sistemas \'Agiles)
\item Vertica bootcamp. (Vertica Systems)
\end{itemize}

\section{Languages}
\cvlanguage{Spanish}{Native}{}
\cvlanguage{English}{Fluent}{B2 according to the \weblink{https://en.wikipedia.org/wiki/Common_European_Framework_of_Reference_for_Languages}{CEFR}.}
\cvlanguage{Portuguese}{Elementary}{A2 according to the \weblink{https://en.wikipedia.org/wiki/Common_European_Framework_of_Reference_for_Languages}{CEFR}.}

\section{Hobbies}
\cvlistitem{Programming, member of comunities like
\weblink{http://python.org.ar/pyar/}{Python Argentina}, in the 2010 PyCon
Argentina I was an speaker \weblink{https://github.com/cuerty/eacpy}{with a
talk about how to use the CPython API with C and C++ applications}.}
\cvlistitem{Constantly improving my development environment, including my 
favourite editor (Vim) and trying new tools.}
\cvlistitem{Always be learning about new programming languages and
technologies.}
\end{document}

\end{document}
